{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-29 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
\section{Introduction}
    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
    \par 
    A good choice of a minimization algorithm is the Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983}. 
    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
    \begin{align}
        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
        \\
        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
        \\
        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
        \\
        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
    \end{align}\label{eqn:example_algorithm}
    It's well known that if the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
    When $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
    \par
    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has a $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
    \par
    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_k)_{k \ge 1}$. 
    It also has descriptive power to describe several variants of FISTA in the literatures.

@@

        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 

@@

        \todoinline{

@@

                \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm
                beyond Nesterov's rule". 

@@

@@

@@

        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is a $L$ strongly convex function, so it admites quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$: 
        {\footnotesize

@@

        Observe that $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov} with k = 1 so we can invoke Proposition \ref{prop:stepwise-lyapunov}, and it gives: 

@@

        \textcolor{red}
        {
            The choice of $\rho_k$ allows for nontraditional choices of step sizes in the literatures. 
            As we can see from the above convergence claim, there exists choices of $\rho_k\ge 1$ where convergence remains possible. 

@@

\section{Equivalent representations of R-WAPG}
    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
    In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
    This section carries out the tedious but necessary works for demonstrating the descriptive power of R-WAPG. 
    We will formulate it into three generic forms that are commonly seemed in the literatures. 
    These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
    \par 
    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} and finds a representation without using auxiliary sequence $\gamma_k, \hat \gamma_k$. 
    Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:r-wapg-momentum-repr} demonstrates two more equivalent representations of the R-WAPG intermediate form (Definition \ref{def:r-wapg-intermediate}) which are formulated into Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}. 
    Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
    In brief, the relations of these proposition and definitions can be summarized by
    \begin{align*}
        & \text{Definition } \ref{def:wapg} 
        \\
        & \iff 
        \text{Definition } \ref{def:r-wapg-intermediate} & \text{By Proposition }\ref{prop:wapg-first-equivalent-repr}.
        \\
        & \iff \text{Definition }\ref{def:r-wapg-st-form} & \text{By Proposition }\ref{def:r-wapg-st-form}.
        \\
        & \;\implies 
        \text{Definition }\ref{def:r-wapg-momentum-form}. 
        & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}.
    \end{align*}

@@

@@

@@

@@

        \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
            Given any $y_1 = x_1 \in \RR^n$, and sequences $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ Definition \ref{def:rwapg-seq}. 
            The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
                For $k=1, 2,\cdots $
                    & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
                    y_{k + 1} = 
                    \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
            In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
                (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
                = \alpha_{k + 1}(\alpha_k^{-1} - 1).  

@@

           \todo[inline]{Consider adding a remark here on how this is similar in format to the Nesterov's accelerated gradient (2.2.19) in his book. }

@@

        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
            satisfy: 
            \begin{align*}
                y_{k} &= 
                \left(
                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                \right)^{-1}
                \left(
                    v_{k} + 
                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                \right), 
                \\
                x_{k + 1} &= 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proposition}
        \begin{proof}
            From Definition \ref{def:r-wapg-intermediate}, define $(\tau_k, \xi_k, \delta_k)_{k \ge 1}$ in Proposition \ref{prop:abs-st-form} to be
            \begin{align*}
                (\forall k \ge 1) \quad \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu},
                \\
                (\forall k \ge 1)\quad 
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                \\
                (\forall k \ge 1)\quad 
                \delta_k &\defeq \frac{1 + \xi_k}{L\alpha_k}. 
            \end{align*}
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            To see, we have forall $k\ge 1$: 
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Next, it also has for all $k \ge 1$: 
            \begin{align*}
                \frac{1 + \xi_k}{\alpha_k}
                &= 
                \frac{1 + \frac{\mu}{L\alpha_k - \mu}}{\alpha_k}
                = 
                \frac{\frac{L\alpha_k - \mu + \mu}{L \alpha_k - \mu}}{\alpha_k}
                = 
                \frac{L}{L\alpha_k - \mu}.
            \end{align*}
            Hence,  $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$ by Proposition \ref{prop:abs-st-form}.
            Therefore, substituting it gives: 
            \begin{align*}
                v_{k + 1} &= 
                x_{k + 1} + \left(
                    1 + \frac{\mu}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k - \mu}{L\alpha_k}
                \right)\left(
                    \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proof}

@@

\section{R-WAPG describes existing accelerations scheme in the literatures}
    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are descriptive. 
    They generalize many existing sequences used in accelerated proximal gradient schemes. 
    \par
    This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
    \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
        If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
        \begin{enumerate}
            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$. 
        \end{enumerate}
    \end{lemma}
    \begin{proof}
        We start proving (i). 
        For all $k \ge 1$: 
        \begin{align*}
            \alpha_{k + 1}^2 
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 + (\mu/L) \alpha_k
            \\
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 
            \\
            \implies 
            \alpha_{k + 1}^2 
            & \ge (1 - \alpha_{k + 1})\alpha_k^2 
            &  \rho_k \ge 1
            \\
            \iff 
            \alpha_k^{-1} 
            &\ge 
            \alpha_{k + 1}^{-2} + \alpha_{k + 1}^{-1}. 
        \end{align*}
        When $k = 0$, it has $\alpha_0 = 1$. 
        By definition of $\rho_0$ we have 
        \begin{align*}
            \alpha_1^2 &= 
            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 
        \end{align*}
        Therefore (i) holds. 
        (i) is proved. 
        \par
        (i) $\implies$ (ii) because substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
        Solving the equality yields $t_{k + 1} = (1/2)\left(1 \pm \sqrt{1 + 4 t_k^2}\right)$ for all $k \ge 0$. 
        Since $\alpha_k \in (0, 1)$, it means $t_k > 0$, hence the valid root is the larger root which gives the upper bound for $t_{k + 1}$ so: 
        \begin{align*}
            t_{k + 1} \in \left(
                0, \frac{1}{2}\left(1 + \sqrt{1 + 4t_k^2}\right) 
            \right]
        \end{align*}
        To prove (iii), because $\rho_k \ge 1$, we have $\prod_{i = 1}^{k} \max(1, \rho_{k - 1})(1 - 
        \alpha_k)$ for all $k \ge 1 = \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$. 
        By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$: 
        \begin{align*}
            \alpha_k^2 &= \rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2
            \\
            \iff 
            \alpha_k^2/\alpha_{k - 1}^2 &= \rho_{k - 1}(1 - \alpha_k)
            \\
            \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)
            &= 
            \prod_{i = 1}^{k}\alpha_k^2 /\alpha_{k - 1}^2= \alpha_k^2/\alpha_0. 
        \end{align*}
        Because $\alpha_0 = 1$, (iii) is justified. 
    \end{proof}
    \begin{remark}
        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chmabolle, Dossal \cite{chambolle_convergence_2015}. 
    \end{remark}

@@

            & > 1.   & \text{By } a > 2. 

>>>>

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
\section{Introduction}
    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
    \par 
    A good choice of a minimization algorithm is the Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983}. 
    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
    \begin{align}
        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
        \\
        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
        \\
        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
        \\
        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
    \end{align}\label{eqn:example_algorithm}
    It's well known that if the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
    When $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
    \par
    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
    Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
    \par
    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_k)_{k \ge 1}$. 
    It also has descriptive power to describe several variants of FISTA in the literatures.

@@

        In Chambolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 

@@

        \todoinline{\noindent

@@

                \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm beyond Nesterov's rule". 

@@

            \textcolor{red}{The prior works' section is too little, it requires some expansion in the future for sure.} 

@@

        One of the most relevant works is by 
        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.}{\hl{Apidopoulos et al. }\cite{apidopoulos_convergence_2018}}. 
        They showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm. 
        See \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them. }{\cite{attouch_first-order_2022}\cite{maulen_speed_2023}} and references within for  the idea of Hessian Damping used to to stabilize the convergence of the Nesterov's momentum without/with restarting.

@@

        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is an $L$ strongly convex function, so it admits quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$: 
        {\smaller

@@

        Observe that $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov} with $k = 1$, we can invoke Proposition \ref{prop:stepwise-lyapunov}, and it gives: 

@@

        The choice of $\rho_k = 0$ reproduces traditional choice of sequences for the APG algorithm. 
        The above claim showed that there exists $\rho_k > 1$, or $\rho_k < 1$ where convergence of $F(x_k) - F(x^*)$ remains possible. 

@@

\section{Equivalent representations of R-WAPG}
    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
    In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
    This section carries out the tedious but necessary works for demonstrating the descriptive power of R-WAPG. 
    We will formulate it into three generic forms that are commonly seemed in the literatures. 
    These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} and finds a representation without using auxiliary sequence $\gamma_k, \hat \gamma_k$. 
    Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:r-wapg-momentum-repr} demonstrates two more equivalent representations of the R-WAPG intermediate form (Definition \ref{def:r-wapg-intermediate}) which are formulated into Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}. 
    Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
    In brief, the relations of these proposition and definitions can be summarized by
        & \text{Definition } \ref{def:wapg} 
        \text{Definition } \ref{def:r-wapg-intermediate} & \text{By Proposition }\ref{prop:wapg-first-equivalent-repr}.
        & \iff \text{Definition }\ref{def:r-wapg-st-form} & \text{By Proposition }\ref{def:r-wapg-st-form}.
        & \;\implies 
        \text{Definition }\ref{def:r-wapg-momentum-form}. 
        & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}.

@@

    % SECTION INTRODUCTION ENDS 

@@

        Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literatures are stated in the remarks that follows the definitions.

@@

            This form of APG is rarely identified in the literatures. 
            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of 
            \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them. }
            {\hl{in Ryu and Yin's Book} \cite{ryu_large-scale_2022}}, 
            right after Theorem 17. 
            We created this form which makes the math that follows simpler. 
            The inspiration of using this as an intermediate representation was inspired by solving Exercise 12.1 in the same Ryu and Yin's Book. 

@@

@@

            The word similar triangle form can be traced back to several literatures. 
            The term ``Method of Similar Triangle" was used for Algorithm (6.1.19) in Nesterov's book \cite{nesterov_lectures_2018}, but without the necessary graphical illustrations to clarify it. 
            Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
            To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
            \todo{
                $\blacksquare$ Add these. $\blacksquare$ Cite these. 
            }{(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
            \todoinline{\noindent
                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
                For more information, see:  
                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 

        \end{remark}
        \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
            Given any $y_1 = x_1 \in \RR^n$, and sequences $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ Definition \ref{def:rwapg-seq}. 
            The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
            \begin{tcolorbox}
                For $k=1, 2,\cdots $
                \begin{align*}
                    & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
                    \\
                    & 
                    y_{k + 1} = 
                    x_{k + 1} + 
                    \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
                \end{align*}    
            \end{tcolorbox}
            In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
            $$
                (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
                = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
            $$
        \end{definition}
        \begin{remark}
            This format fits with (2.2.19) in Nesterov's book \cite{nesterov_lectures_2018}, however, the sequence $(\alpha_k)_{k \ge 0}$ would be given by a different rule. 
            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} to see a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.
        \end{remark}

@@

        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
            satisfy: 
            \begin{align*}
                y_{k} &= 
                \left(
                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                \right)^{-1}
                \left(
                    v_{k} + 
                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                \right), 
                \\
                x_{k + 1} &= 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proposition}
        \begin{proof}
            From Definition \ref{def:r-wapg-intermediate}, define $(\tau_k, \xi_k, \delta_k)_{k \ge 1}$ in Proposition \ref{prop:abs-st-form} to be
            \begin{align*}
                (\forall k \ge 1) \quad \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu},
                \\
                (\forall k \ge 1)\quad 
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                \\
                (\forall k \ge 1)\quad 
                \delta_k &\defeq \frac{1 + \xi_k}{L\alpha_k}. 
            \end{align*}
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            To see, we have for all $k\ge 1$: 
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Next, it also has for all $k \ge 1$: 
            \begin{align*}
                \frac{1 + \xi_k}{\alpha_k}
                &= 
                \frac{1 + \frac{\mu}{L\alpha_k - \mu}}{\alpha_k}
                = 
                \frac{\frac{L\alpha_k - \mu + \mu}{L \alpha_k - \mu}}{\alpha_k}
                = 
                \frac{L}{L\alpha_k - \mu}.
            \end{align*}
            Hence,  $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$ by Proposition \ref{prop:abs-st-form}.
            Therefore, substituting it gives: 
            \begin{align*}
                v_{k + 1} &= 
                x_{k + 1} + \left(
                    1 + \frac{\mu}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k - \mu}{L\alpha_k}
                \right)\left(
                    \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proof}

@@

\section{R-WAPG describes existing accelerations scheme in the literatures}
    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are descriptive. 
    They generalize many existing sequences used in accelerated proximal gradient schemes. 
    \par
    This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
    \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
        If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
        \begin{enumerate}
            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$. 
        \end{enumerate}
    \end{lemma}
    \begin{proof}
        We start proving (i). 
        For all $k \ge 1$: 
        \begin{align*}
            \alpha_{k + 1}^2 
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 + (\mu/L) \alpha_k
            \\
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 
            \\
            \implies 
            \alpha_{k + 1}^2 
            & \ge (1 - \alpha_{k + 1})\alpha_k^2 
            &  \rho_k \ge 1
            \\
            \iff 
            \alpha_k^{-1} 
            &\ge 
            \alpha_{k + 1}^{-2} + \alpha_{k + 1}^{-1}. 
        \end{align*}
        When $k = 0$, it has $\alpha_0 = 1$. 
        By definition of $\rho_0$ we have 
        \begin{align*}
            \alpha_1^2 &= 
            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 
        \end{align*}
        Therefore, (i) holds. 
        (i) is proved. 
        \par
        (i) $\implies$ (ii) because substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
        Solving the equality yields $t_{k + 1} = (1/2)\left(1 \pm \sqrt{1 + 4 t_k^2}\right)$ for all $k \ge 0$. 
        Since $\alpha_k \in (0, 1)$, it means $t_k > 0$, hence the valid root is the larger root which gives the upper bound for $t_{k + 1}$ so: 
        \begin{align*}
            t_{k + 1} \in \left(
                0, \frac{1}{2}\left(1 + \sqrt{1 + 4t_k^2}\right) 
            \right]
        \end{align*}
        To prove (iii), because $\rho_k \ge 1$, we have $\prod_{i = 1}^{k} \max(1, \rho_{k - 1})(1 - 
        \alpha_k)$ for all $k \ge 1 = \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$. 
        By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$: 
        \begin{align*}
            \alpha_k^2 &= \rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2
            \\
            \iff 
            \alpha_k^2/\alpha_{k - 1}^2 &= \rho_{k - 1}(1 - \alpha_k)
            \\
            \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)
            &= 
            \prod_{i = 1}^{k}\alpha_k^2 /\alpha_{k - 1}^2= \alpha_k^2/\alpha_0. 
        \end{align*}
        Because $\alpha_0 = 1$, (iii) is justified. 
    \end{proof}
    \begin{remark}
        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chambolle, Dossal \cite{chambolle_convergence_2015}. 
    \end{remark}

@@

            & > 1.   & \text{By } a \ge 2. 
